What is the impact of weather catastrophe frequency and severity on property insurance policy prices, and how can homeowners alleviate financial strain?

### 2023-10-30 manuscript/manuscript.tex
results added

\section{Results}
\label{sec:resu}

>>>>

\section{Results}
\label{sec:resu}
\subsection{Summary Statistics}
Table 1 \ref{tab:summary} presents summary statistics for the premium and disaster data. The disaster measures show substantial variability, 
highlighting the irregular nature of extremes. Hurricane and flooding perils account for the largest share of overall cost and 
insured losses.

\begin{table}[h]
    \label{tab:summary}
      \centering
      \begin{tabular}{|l|c|c|c|}
          \hline
          & Mean & SD & Range \\
          \hline
          Premium & \textdollar 832 & \textdollar 196 & \textdollar 444 - \textdollar 1,832 \\
          Number of Disasters & 1.90 & 2.05 & 0 - 13 \\
          Total Cost (\textdollar) & 3.04B & 8.60B & 0 - 65.0B \\
          Insured Losses (\textdollar) & 1.35B & 5.03B & 0 - 37.3B \\
          \hline
      \end{tabular}
      \caption{Summary Statistics}
  \end{table}

Figure 1 \ref{fig:premium_trend} shows the upward national trend in average homeowners premiums, along with key major hurricanes. Premium growth accelerated 
starting in the mid-2000s, corresponding with damaging hurricane seasons.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.8\linewidth]{premium_trend.pdf}
    \caption{Average Homeowners Insurance Premiums and Major Hurricanes}
    \label{fig:premium_trend}
\end{figure}

\subsection{Regression Results}
Table 2 \ref{tab:reg_results} presents results from the panel regressions. The number of disasters and total cost are significantly associated with 
higher premiums based on the log-log specification. A 10\% increase in disasters corresponds to a 0.6\% rise in premiums. Meanwhile, 
a 10\% rise in total damage leads to a 0.04\% premium increase.

\begin{table}[h]
    \label{tab:reg_results}
      \centering
      \begin{tabular}{|l|c|c|c|}
          \hline
          & (1) & (2) & (3) \\
          \hline
          Log(Number Disasters) & 0.062$^*$ & & \\
          & (0.018) & & \\
          Log(Total Cost) & & 0.004$^*$ & 0.005$^*$ \\
          & & (0.002) & (0.002) \\
          Log(Insured Loss) & & & 0.002 \\
          & & & (0.003) \\
          \hline
          State FE & \checkmark & \checkmark & \checkmark \\
          Year FE & \checkmark & \checkmark & \checkmark \\
          Observations & 756 & 756 & 756 \\
          $R^2$ & 0.936 & 0.935 & 0.935 \\
          \hline
      \end{tabular}
      \caption{Disaster Effects on Homeowners Premiums}
  \end{table}

The results by peril type in Table 3 \ref{tab:reg_peril} show hurricane and flood disasters have the most significant effects. A 10\% increase in 
hurricane or flood damage correlates with around a 0.01\% rise in premiums. Severe storms and winter weather also show positive 
effects. Wildfires and earthquakes appear less influential, likely due to their more limited geographic footprints.

\begin{table}[h]
  \label{tab:reg_peril}
    \centering
    \begin{tabular}{|l|c|c|c|c|}
        \hline
        & (1) & (2) & (3) & (4) \\
        \hline
        Log(Hurricane Cost) & 0.010$^*$ & & & \\
        & (0.003) & & & \\
        Log(Flood Cost) & & 0.013$^*$ & & \\
        & & (0.004) & & \\
        Log(Severe Storm Cost) & & & 0.006$^*$ & \\
        & & & (0.003) & \\
        Log(Winter Cost) & & & & 0.011$^{**}$ \\
        & & & & (0.005) \\
        \hline
        State FE & \checkmark & \checkmark & \checkmark & \checkmark \\
        Year FE & \checkmark & \checkmark & \checkmark & \checkmark \\
        Observations & 756 & 756 & 756 & 756 \\
        $R^2$ & 0.935 & 0.935 & 0.935 & 0.935 \\
        \hline
    \end{tabular}
    \caption{Disaster Effects by Peril}
\end{table}
